### 2018-07-21 paper/spor.tex
Renames global-overlay-design to spor
Writes up SPOR

\subsection{\Acf*{SPOR}}%
\label{SPOR}%
\label{sec:global_overlay}%
\label{sec:message_passing}%

@@

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\avail_d(t)\) is the node's probability of being online as a function 
    of time.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}.
But even a solution like Tor's authoritative directory servers would work,

\commentDaniel{We should describe how to do this selection using a prediction 
  oracle, then we provide a prediction oracle later.}
\commentDaniel{The stuff below is just as before, it must be edited.}

\newcommand{\viewsize}{\ensuremath{l_{\text{view}}\xspace}}
\newcommand{\view}{\ensuremath{\mathcal{V}_{\text{RPS}}\xspace}}
\NewAlgorithm{\GetRandomNode}{\text{random descriptor from }\view}

To create PORs, devices need to know the address, encryption key, and probability of remaining available of some nodes in the system, to pick them as relays on the route.

To reach this goal, we employ Random Peer Sampling (RPS)~\cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
Essentially, each node maintains a view \view containing \viewsize other devices' descriptors. 
This view is periodically updated as follows: a device $d$ pops the oldest descriptor $d'$ from its view, then swaps a predefined number of $l$ elements from \view with $d'$.
Both devices add a descriptor for themselves to the view exchange.
If $d'$ was offline, its descriptor is simply removed from the $d$'s view, but \view is otherwise not updated.

This allows for two things: firstly, each device's view contains a constantly changing random sample of the whole set of devices;
secondly, offline nodes get removed from one's view fairly fast---we can say that a \view contains \emph{mostly} descriptors of online devices.

\NewVariable{\pk}{pk}

% \commentDaniel{%
%   What is the probability distribution of the peer sample that we get?
%   Will it be close to uniformly random?
%   I need this for the security analysis.%
% }

% Every time a device is online, it participates in the random peer sampling 
% protocol.
% If a device is sampled it provides the following information:
% \begin{itemize}
%   \item its address, $@_d$;
%   \item its public key, \(\pk_d\);
%   \item the probability of being online, $p_d=P\left[d \in O_{t+1} | S_t\right] $.
% \end{itemize}
% We will denote this by the following algorithm $(@_d, \pk_d, p_d)\gets 
%   \GetRandomNode$, which will be used below.
% The probability of being online, \(p_d\), is inferred as above 
% (\ref{sub:a_model_of_the_user_s_behavior}).

>>>>

\subsection{\Acf*{SPOR}}%
\label{SPOR}%
\label{sec:SPOR}%
\label{sec:message_passing}%

@@

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\avail_d(t)\) is the node's probability of being online as a function 
    of time.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}.
But even a solution like Tor's authoritative directory servers would work,
We will treat \(\avail_d\) in \cref{SPORES}.

When Bob runs \(\CreateReply\) (or Alice runs \(\CreateFwd\)) he must supply a 
set of nodes for each layer of the route, \(L = \{L_0, \dotsc, L_\nu\}\), where 
\(|L_i| \leq w_L\) for \(0\leq i\leq \nu\).
The set \(L_\nu\) contains only one or more of Bob's devices.
For the other layers, \(L_i\) for \(i < \nu\), Bob will do the following:
Bob queries \(\GetRandomNode\) \((\nu-1)\cdot w_L\) times to get enough nodes 
to fill all remaining layers.
Bob will distribute these nodes across all layers \(L_i\) to maximize \(\min_i 
  \avail_{L_i}(t)\), where \(\avail_{L_i}(t) = 1-\prod_{l\in L_i} 
  (1-\avail_l(t))\).
This means that Bob minimizes the risk of a layer (\ie all nodes in a layer) 
being unavailable.
